---
title: "Economic Demography"
subtitle: "Introduction to R"
author: "Andriy Zhubryd"
date: "10 července 2016"
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap, interactive]         # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_idgets     : {rCharts: ["libraries/highcharts", "libraries/nvd3", "libraries/morris"]} 
output: 
  html_document: 
    fig_width: 12
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

R is not just big scary console window, where you need to enter you code. It can also be a nice [report](http://www.zubrand.github.io/R-Tutorial) or [presentation](http://www.zubrand.github.io/R-Tutorial/Presentation).

This is a simple example how you can communicate your results from R in the form of presentation, which you can open in your web browser without a need to install R.

One of the greatest advantage of such presentation is automation and reproducibility. If you change some input data or some part of your algorithm, R will automatically generate new presentation and manual actions of copy-pasting results in presentation are avoided. Also, if you need your results to be reproducible, R presentation is definitely for you.

```{r preparation, echo=FALSE, message=F}
library(dplyr, warn.conflicts = F)
library(reshape2)
library(scales)
library(ggplot2)
library(pyramid)
library(xtable)
library(rCharts)
library(googleVis, warn.conflicts = F)
dt_pyramid <- read.csv('Data/dt_pyramid.csv')
```

---

## Show your calculations


```{r indeces}
# Index of masculinity
Ratios <- dt_pyramid %>% 
       filter(Geo %in% c("CZ","ES","NO","SE","DE_TOT") & between(Year, 2000, 2010)) %>%
       group_by(Year, Geo) %>% summarize(Masculinity = sum(M)/sum(F))
# Sauvy's index
     Ratios <- dt_pyramid %>% mutate(Tot = M + F) %>% group_by(Year, Geo, Gen_bio) %>% 
       summarize(Tot = sum(Tot)) %>% 
       dcast(Year + Geo ~ Gen_bio, value.var = "Tot", fun.aggregate = sum, na.rm = T) %>%
       setNames(c("Year", "Geo", "I", "II", "III")) %>% mutate(Sauvy = III/I) %>%
       select(Year, Geo, Sauvy) %>% merge(Ratios)
# Indeces for economical generations
     Ratios <- dt_pyramid %>% mutate(Tot = M + F) %>% group_by(Year, Geo, Gen_eco) %>% 
       summarize(Tot = sum(Tot)) %>% 
       dcast(Year + Geo ~ Gen_eco, value.var = "Tot", fun.aggregate = sum, na.rm = T) %>%
       setNames(c("Year", "Geo", "I", "II", "III")) %>% 
       mutate(TDR = (I+III)/II, OADR = III/II, JADR = I/II, Seniority = III/I) %>% 
       select(-I,-II,-III) %>% merge(Ratios)
```

---

## Show your results

```{r ratios, echo=F, results='asis'}
Ratios %>% head(13) %>% xtable(digits = 3) %>% print(type = 'html')
```

---

## Visualize your resuls

```{r pyramid, echo = F, fig.width=12}
dt_pyramid %>% filter(Geo == "CZ" & Year == 2000) %>% select(M, F, Age) %>%
  pyramid(Csize = 1, Cstep = 5, AxisFM = 'd', Cgap = .1, Laxis = 0:4*25000,
          main = "Pyramid of Czech population in 2000")
```

---

## Compare your results

```{r ggplot2, echo = F, fig.width=12, message=F}
tmp_pyr <- dt_pyramid %>% filter(Geo %in% c("CZ","BE") & Year %in% c(2000, 2010)) %>%
  select(-X, -Gen_bio, -Gen_eco) %>% melt(id = c("Age", "Geo", "Year")) %>%
  mutate(Sex = variable, Population = value, Age = Age - Age %% 5) %>% group_by(Age, Geo, Year, Sex) %>% summarize(Population = sum(Population))
ggplot(data = tmp_pyr, aes(x = Age, y = Population, fill = Sex)) + 
  geom_bar(data = subset(tmp_pyr, Sex == "F"), stat = "identity") + 
  geom_bar(data = subset(tmp_pyr, Sex == "M"), aes(y=-Population), stat = "identity") + 
  scale_y_continuous(labels = function(x) comma(abs(x))) + 
  coord_flip() + ggtitle("Pyramid graphs of selected years and countries\n5-year grouping") +
  scale_fill_brewer(palette = "Set1") +
  facet_grid(Geo ~ Year) + theme_bw()
```

---

## Interact with your results

```{r rcharts, results='asis', comment = NA, echo = F, tidy=F, message=T}
library(rCharts)
options(
  rcharts.mode = 'iframesrc', 
  rcharts.cdn = TRUE,
  RCHART_WIDTH = 1000,
  RCHART_HEIGHT = 500
)

tmp <- dt_pyramid %>% filter(Geo == "CZ") %>% 
  group_by(Gen_eco, Year) %>% summarize(Population = sum(F+M)) %>%
  mutate(Generation = Gen_eco, Date = as.numeric(as.POSIXct(paste0(Year, "-01-01"))))
r <- nPlot(Population ~ Year, group = "Generation", data = tmp %>% filter(Year >= 1990), type = 'stackedAreaChart', id = 'nPlot1')
r$set(title = "Development of economical generation in Czech Republic")
r$setTemplate(afterScript='<style> svg text {font-size: 9px;}</style>')
r$yAxis(staggerLabels = FALSE)

r$print('chartr', include_assets=TRUE, cdn=TRUE)
```

--- &interactive

## Play with your results

```{r gvis2, results='asis', comment=NA, message=F, echo=F, opts.label = 'interactive'}
M <- gvisMotionChart(Ratios, idvar = "Geo", timevar = "Year", options = list(width = 100, height = 500), chartid = "chartid")
print(M, 'chart')
```

--- &radio

## Interact with your readers 

Will you use R in the future?

1. _Yes_
2. _Definitely_
3. No
4. Not sure

*** .hint 
I'm sure you know the right answer.

*** .explanation
It's obvious, isn't it?


